Batch Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-02-07 paper/experiments.tex
Paper update

\begin{table}[htbp]
    \centering
    \caption{Summary of the analytical benchmark functions}
    \label{tab:summaryanalygical}
    \begin{tabular}{llllllll}
        \toprule
         Function           & Dimension        & Search domain             \\ \midrule
         Branin             & 2                & $[-5,  10]\times[0, 15]$  \\
         Alpine1            & 5                & $[-10, 10]^5$             \\
         Hartmann6          & 6                & $[0,   1]^6$              \\
         Eggholder          & 2                & $[-512, 512]^2$           \\
         Ackley2            & 2                & $[-32, 32]^2$             \\
         Ackley10           & 10               & $[-32, 32]^{10}$          \\
         Rosenbrock2        & 2                & $[-5,  10]^2$             \\
         Rosenbrock10       & 10               & $[-20, 20]^{10}$          \\
        \bottomrule
    \end{tabular}
\end{table}

@@

The mean convergence plot is shown in Figure~\ref{fig:CovPlotBenchmark}. The
statistics of the final optimization results are listed in
Table~\ref{tab:result_analytical}. As can be seen, when running with batch size
$B = 4$, the MACE algorithm gives the best performance for six out of the eight
benchmarks.  For the 2D Ackley function, EI-LP is the best algorithm, while for
the Eggholder function, the MACE, BLCB, and EI-LP have quite similar
performance.  Compare the batch MACE and the sequential MACE, the speedup is
also dramatic.

% \begin{table*}[tp]
%     \tiny
%     \centering
%     \caption{Optimization results of the benchmark functions}
%     \label{tab:result_analytical}
%     \begin{tabular}{lllllllllll}
%         \toprule
%         Function    & MACE-1             & LCB-1                 &  EI-1                 &  MACE-4               & BLCB-4                &  EI-LP-4              & qKG-4                   & qEI-4                     \\ \midrule
%         Eggholder   & 88$\pm$76          &  1.5e+2$\pm$1.1e2     &  1.7e2$\pm$1.3e2      &  46$\pm$41            &  57$\pm$36            &  45$\pm$56            &  1.1e2$\pm$68  &  72$\pm$52            & \\
%         Branin      & 1e-5$\pm$1.3e-5    &  6.9e-5$\pm$1.1e-4    &  0.016$\pm$0.016      &  4.6e-6$\pm$6.6e-6    &  4.3e-5$\pm$6.3e-5    &  0.021$\pm$0.018      &  0.27$\pm$0.27 &  3.3e-4$\pm$1.1e-3    & \\
%         Alpine1     & 2.7$\pm$1.1        &  5.7$\pm$1.8          &  2.5$\pm$1.6          &  0.9$\pm$0.84         &  1.9$\pm$0.94         &  1$\pm$0.46           &  3$\pm$1.1     &  2.7$\pm$1.1          & \\
%         Hart6       & 0.065$\pm$0.062    &  0.13$\pm$0.12        &  0.11$\pm$0.15        &  0.028$\pm$0.052      &  0.064$\pm$0.062      &  0.054$\pm$0.056      &  0.47$\pm$0.19 &  0.19$\pm$0.12        & \\
%         Ackley      & 1.7$\pm$1.1        &  1.6$\pm$0.93         &  1$\pm$0.99           &  1.1$\pm$0.89         &  1.4$\pm$1            &  0.28$\pm$0.25        &  5.6$\pm$1.8   &  2.9$\pm$1            & \\
%         Rosenbrock  & 0.026$\pm$0.051    &  0.02$\pm$0.021       &  14$\pm$9.5           &  9.5e-4$\pm$9.4e-4    &  1.9e-3$\pm$1.8e-3    &  2.7$\pm$2.1          &  5$\pm$3.7     &  10$\pm$15            & \\
%         G05         & 3.1$\pm$0.45       &  3.1$\pm$0.52         &  19$\pm$0.65          &  2.6$\pm$0.54         &  3.3$\pm$0.74         &  18$\pm$0.61          &  18$\pm$0.76   &  18$\pm$0.5           & \\
%         G07         & 500$\pm$300        &  520$\pm$290          &  1400$\pm$640         &  160$\pm$50           &  410$\pm$130          &  720$\pm$330          &  710$\pm$410   &  660$\pm$340          & \\
%         \bottomrule
%     \end{tabular}
% \end{table*}

@@

\begin{figure}[h]
    \begin{center}
        \centerline{\includegraphics[width=\columnwidth]{./img/sopam.pdf}}
        \caption{Schematic of the operational amplifier}
        \label{fig:schDAC2014}
    \end{center}
\end{figure}

@@

\begin{table}[h]
    \centering
    \caption{Optimization results of the operational amplifier}
    \label{tab:result_opamp}
    \begin{tabular}{llll}
        \toprule
        Algorithm & Results     \\ \midrule
        MACE-1    & 0.0$\pm$0.0 \\
        LCB-1     & 0.0$\pm$0.0 \\
        EI-1      & 0.0$\pm$0.0 \\
        MACE-4    & 0.0$\pm$0.0 \\
        BLCB-1    & 0.0$\pm$0.0 \\
        EI-LP-4   & 0.0$\pm$0.0 \\
        \bottomrule
    \end{tabular}
\end{table}

The mean convergence plot for the sequential and batch runs are plotted in
Figure~\ref{fig:resDAC2014}. As can be seen, the MACE algorithm gave better
solution compared with other algorithms, the sequential MACE algorithm found
better solution than BLCB and EI-LP with batch size $B = 4$, which showed that
the multi-objective acquisition ensemble is more robust than relying on single
acquisition function; compared with the sequential MACE algorithm, the MACE
algorithm with batch size $B = 4$ showed considerable speedup.

@@

\begin{figure}[htbp]
    \begin{center}
        \centerline{\includegraphics[width=\columnwidth]{./img/classE.eps}}
        \caption{Schematic of the power amplifier}
        \label{fig:schPA}
    \end{center}
\end{figure}

@@

\begin{table}[htbp]
    \centering
    \caption{Optimization results of the power amplifier}
    \label{tab:result_PA}
    \begin{tabular}{llll}
        \toprule
        Algorithm & Results     \\ \midrule
        MACE-1    & 0.0$\pm$0.0 \\
        LCB-1     & 0.0$\pm$0.0 \\
        EI-1      & 0.0$\pm$0.0 \\
        MACE-4    & 0.0$\pm$0.0 \\
        BLCB-1    & 0.0$\pm$0.0 \\
        EI-LP-4   & 0.0$\pm$0.0 \\
        \bottomrule
    \end{tabular}
\end{table}

@@

\begin{figure}[htbp]
\vskip 0.2in
\begin{center}
\centerline{\includegraphics[width=\columnwidth]{./img/ClassE_mean.eps}}
\caption{Optimization results of the class-E power amplifier}
\label{fig:resClassE}
\end{center}
\vskip -0.2in
\end{figure}

>>>>

\begin{table}[htbp]
    \centering
    \caption{Summary of the analytical benchmark functions}
    \label{tab:summaryanalygical}
    \begin{tabular}{llllllll}
        \toprule
         Function           & Dimension        & Search domain             \\ \midrule
         Branin             & 2                & $[-5,  10]\times[0, 15]$  \\
         Alpine1            & 5                & $[-10, 10]^5$             \\
         Hartmann6          & 6                & $[0,   1]^6$              \\
         Eggholder          & 2                & $[-512, 512]^2$           \\
         Ackley2            & 2                & $[-32, 32]^2$             \\
         Ackley10           & 10               & $[-32, 32]^{10}$          \\
         Rosenbrock2        & 2                & $[-5,  10]^2$             \\
         Rosenbrock10       & 10               & $[-20, 20]^{10}$          \\
        \bottomrule
    \end{tabular}
    \vskip -0.2in
\end{table}

@@

The mean performances of the tested algorithms on the benchmark functions are
plotted in Figure~\ref{fig:CovPlotBenchmark}, the statistics of the final
optimization results are listed in Table~\ref{tab:result_analytical}. As can be
seen in Figure~\ref{fig:CovPlotBenchmark} and
Table~\ref{tab:result_analytical}, when running in sequential mode, the MACE
algorithm is competitive with the LCB and EI acquisition functions, the MACE-1
algorithm gave better performances than EI-1 and LCB-1 in the Eggholder,
Branin, Hartmann6, Ackley10, and Rosenbrock10 functions; also, the parallel
MACE (MACE-4) gave the best performances among all the tested algorithms for
six out of the eight benchmark functions, and has shown dramatic speedup
compared to the sequential MACE (MACE-1).

% when running with batch size $B = 4$, the
% MACE algorithm gives the best performance for six out of the eight benchmarks.
% For the 2D Ackley function, EI-LP is the best algorithm, while for the
% Eggholder function, the MACE, BLCB, and EI-LP have quite similar performance.
% Compare the batch MACE and the sequential MACE, the speedup is also dramatic.

@@

\begin{figure}[h]
    \begin{center}
        \centerline{\includegraphics[width=\columnwidth]{./img/sopam.pdf}}
        \caption{Schematic of the operational amplifier}
        \label{fig:schDAC2014}
    \end{center}
    \vskip -0.2in
\end{figure}

@@

\begin{table}[h]
    \centering
    \caption{Optimization results of the operational amplifier}
    \label{tab:result_opamp}
    \begin{tabular}{llll}
        \toprule
        Algorithm & Results     \\ \midrule
        MACE-1    & -678.174$\pm$21.7445 \\
        LCB-1     & -607.583$\pm$51.9786 \\
        EI-1      & -532.555$\pm$66.942  \\
        MACE-4    & \textbf{-690.3$\pm$0.104963}  \\
        BLCB-4    & -665.442$\pm$23.066  \\
        EI-LP-4   & -636.675$\pm$35.7359 \\
        \bottomrule
    \end{tabular}
\end{table}

The mean convergence plot for the sequential and batch runs are given in
Figure~\ref{fig:resDAC2014}, the mean and standard deviation of the final
optimized FOM values are listed in Table~\ref{tab:result_opamp}. As can be
seen, on average, the batch MACE algorithm had the fastest convergence rate
compared with the sequential MACE algorithm and other parallel algorithms. It
should also be noted that the final optimized FOM values given by MACE-4 have
very small deviation (0.105) compared with other algorithms.

% The mean convergence plot for the sequential and batch runs are shown in
% Figure~\ref{fig:resDAC2014}. As can be seen, the MACE algorithm gave better
% solution compared with other algorithms, the sequential MACE algorithm found
% better solution than BLCB and EI-LP with batch size $B = 4$, which showed that
% the multi-objective acquisition ensemble is more robust than relying on single
% acquisition function; compared with the sequential MACE algorithm, the MACE
% algorithm with batch size $B = 4$ showed considerable speedup.

@@

\begin{table}[]
    \centering
    \caption{Optimization results of the power amplifier}
    \label{tab:result_PA}
    \begin{tabular}{llll}
        \toprule
        Algorithm & Results               \\ \midrule
        MACE-1    & -4.08608$\pm$0.296647 \\
        LCB-1     & -3.78533$\pm$0.335532 \\
        EI-1      & -3.36407$\pm$0.307489 \\
        MACE-4    & \textbf{-4.31762$\pm$0.347026} \\
        BLCB-4    & -4.20266$\pm$0.211102 \\
        EI-LP-4   & -4.07233$\pm$0.244436 \\
        \bottomrule
    \end{tabular}
    \vskip -0.2in
\end{table}

\begin{figure}[]
    \begin{center}
        \centerline{\includegraphics[width=\columnwidth]{./img/classE.eps}}
        \caption{Schematic of the power amplifier}
        \label{fig:schPA}
    \end{center}
\end{figure}

@@

@@

\begin{figure}[]
    \begin{center}
        \centerline{\includegraphics[width=\columnwidth]{./img/ClassE_mean.eps}}
        \caption{Optimization results of the class-E power amplifier}
        \label{fig:resClassE}
    \end{center}
    \vskip -0.2in
\end{figure}
